A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-03-15 main.tex
Updates from Overleaf
grammarly checked

%=================================================================
% Journal of Personalized Medicine, JPM
\documentclass[jpm,article,submit,moreauthors,pdftex]{Definitions/mdpi}
\maxdeadcycles=500 % Output loop---200 consecutive dead cycles.

@@

\subsubsection{Holistic cancer care} 
% carcinogenesis by epigenetic control (placebo/nocebo), Bruce Lipton introduced mind-brain-body system. (gene expression is not an independent $X_mrna$, which is correlated with other $X_body, X_stress, X_inflammation, X_ros$)
% cancer care with person-central approach, PCA; Cullen, Carl Rogers

@@

%discussion: the third limitation
There are eighty one ($X_1 ... X_81$) physical, pathological and social conditions derived from participants available for survival modelling in the TCGA, 
% since it has comprehensive clinical features, 
such as age, gender, residual tumor, vital status, days\_to\_last\_followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
However, the TCGA did not collect other features from holistic cancer care.
% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equal important comparing with physical and social status.
%
World Health Organisation has called worldwide for delivering people-centred (or person-centred) care from the physical, emotional, socioeconomic and spiritual perspectives\cite{WHO2015}\cite{Ling-ChengMong2021}.
Core principles can be taken to achieve people-centred and integrated health service delivery. 
First principle is holistic – focusing on physical, socioeconomic, mental and emotional well-being. 
Holistic care is defined that care and see the person as a whole with psychological, social and environmental levels of needs and goals.
%that considers  factors rather than just the symptoms of disease or ill-health.
Second principle is empowering – supporting people to manage and take responsibility for their own health,
%Empowerment: the process of supporting people and communities to take control of their own health needs resulting, 
for example, in the uptake of healthier behaviours or the ability to self-manage illnesses.
People-centred care requires that people have the education and support they need to make decisions and participate in their own care.
%Glossary:
%People-centred care: an approach to care that consciously adopts individuals’, carers’, families’ and communities’ perspectives as participants in, and beneficiaries of, trusted health systems that respond to their needs and preferences in humane and holistic ways. People-centred care also requires that people have the education and support they need to make decisions and participate in their own care. It is organized around the health needs and expectations of people rather than diseases (7,8) 
%Person-centred care: care approaches and practices that see the person as a whole with many levels of needs and goals, with these needs coming from their own personal social determinants of health.
%(1. World Health Organization. WHO global strategy on people-centred and integrated health services: interim report. https://apps.who.int/iris/handle/10665/155002 (2015).)

@@

The spiritual care is the key of holistic healthcare in dental practice\cite{Ling-ChengMong2021} and cancer patient care\cite{Hulett2016}. 
Being mindful to patient’s mental health, emotional changes, socioeconomic during healthcare. %Taking patient’s socioeconomic statement and supporting system thoroughly for building a holistic consideration. 
Learning to listen proactively.
Being aware of patient’s spiritual needs.

@@

Mindfulness-Based Stress Reduction (MBSR) program has been introduced by Jon Kabat-Zinn in 1979\cite{Niazi2011}. MBSR composes the contemplative, spiritually based Buddhist philosophy, which promotes the development of a nonjudgmental, accepting, and patient worldview and teaches relaxation through focused awareness on breathing during meditation. It employs (static) mindfulness meditation to alleviate suffering associated with physical (pain), psychosomatic and psychiatric disorders.

@@

This impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
Thus, cortisol is one of the most common (objective) outcome studied in psychoneuroimmunological (PNI) factors. % others: interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV
The standardized, psychosocial (subjective) measures includes depression, stress, quality of life, anxiety, fatigue, mindfulness, mood and specific spiritual growth (ie, meaning of life)\cite{Hsiao2012}. %  body-mind-spirit (BMS) group therapy in the Meaning in Life questionnaire (MLQ) including two sub-scales: MLQ-Presence and MLQ-Search.

@@

This review revealed a positive pattern between spiritually based interventions and a number of PNI biomarker outcomes, suggesting that spiritually based interventions offer positive mental and physiological health benefits. For breast cancer survivors, these studies suggested that engaging in spiritually based practices may improve or stabilize the immune profile dysregulation that occurs with breast cancer.\cite{Hulett2016}.

@@

A randomized clinical trial with active control proved that early provision of MBSR for women newly diagnosed with breast cancer provides psychological benefits (reduction of stress, fatigue, sleep disturbance, and depressive symptoms), and also optimizes immune functions (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) supportive of cancer survival.\cite{WitekJanusek2019}

%%%% PCA and ECA: the way to delivery of MBSR
Therapeutic relationship is an essence towards spiritual care.
According to my 17-year clinical experience of healthcare, sometimes patient could tell me: "how amazing it is, I would like to talk about myself more when I visit this doctor who I trust".
In 1979, Rogers wrote: "I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing. Then simply my presence is releasing and helpful."\cite{Rogers1979}
Carl Rogers developed person-centered theory that the therapist is providing the appropriate social-environmental conditions for their patients\cite{Rogers1957}\cite{Joseph2004}\cite{Griffiths2013}.
Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers in 1957\cite{Rogers1957}:\\
%For constructive personality change to occur, it is necessary that these conditions exist and continue over a period of time: 
1. Two persons are in psychological contact. \\
2. The first, whom we shall term the client, is in a state of incongruence (or not harmony), being vulnerable or anxious. \\
3. The second person, whom we shall term the therapist, is congruent
or integrated in the relationship. \\
4. The therapist experiences "unconditional positive regard" for the client. \\
5. The therapist experiences an empathic understanding of the client's
internal frame of reference and endeavors to communicate this experience to the client. \\
6. The communication to the client of the therapist's empathic understanding and unconditional positive regard is to a minimal degree achieved.\\
%empowering
%(一)雙方有心理的接觸。
%(二)當事人正感到焦慮或不一致(incongruence)。 
%(三)治療者在治療關係中是一致的 (congruence, agreement or harmony; compatibility)、真實的或真誠的。
%(四)治療者能夠對當事人表現出無條件的關懷。無條件關懷(不批判/頓悟)
%(五)治療者能夠同理的瞭解當事人的內在，並努力傳達「我懂你的」。
%(六) 第五點只要有個適當的開始，療癒就會開始
%Dealing with negative emotions. 情緒影響，造成焦慮、發炎、免疫 Cancer
As the cancer patient feels intense negative emotions of extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, 
%七情: 喜、怒、思、悲、恐、驚、憂
depression, fatigue, stress, it is not the patient-centred therapist’s task to remove these feelings: the task is simply to stay with the patient’s experiences. 
% 只是陪伴
%The research implication is to investigate the necessity and sufficiency of the six conditions.
%Rogers, C. R. A Theory of Therapy, Personality, and Interpersonal Relationships: As Developed in the Client-centered Framework. in Psychology: A Study of a Science. Study 1, Volume 3: Formulations of the Person and the Social Context (ed. Koch, S.) 184–256 (McGraw Hill, 1959).\cite{Rogers1959}
%PCA理論 by *** Tex Chi
%治療關係的六核心條件: 說好話 眼對眼 engaging 用真心
%以心印心 engaging
%身心相連 body-mind connection
%捨末求本 find the source: emotion
A holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection. Their empathy, sympathy, and compassion is induced by the suffering of patients from those diseases. They will try to treat patients by medication therapy, surgery, and "themselves".
The resilience of patients will be induced by unconditional positive regard. % of healing.
Thus, patients will trust them who take care of and have confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner.
%身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
%「把自己當藥方開出去」
%Spirituality
%慈悲心 compassion 
%同情心 sympathy
%同理心 empathy
%non-verbal contact

@@

%% why holistic? % Environment 環境 => 分享權力、 自決 empowering
The WHO's second principle is empowering – supporting people to manage and take responsibility for their own health.
Bruce Lipton introduced mind-brain-body system in 1992\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}.
%Lipton 1992, epinephrine and histamine signals in endothelium, %心智作用
In a state of fear, the brain releases chemicals associated with fear, which are stress hormones and inflammatory cytokines.
In the other state of love, dopamine, oxytocin, vasopressin, and growth hormone will be released by central nerve system in response to the perception of love.
%Bruce Lipton: the biology of belief %信念的力量 \cite{Lipton2015}
%placebo effect and the old belief of genetic determinism\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}
%biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
%那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。
%% 1. Kobisi, W. Mind inhibitors. in The 30th International Congress Of The World Federation Of Hemophilia, July 8‐12 vol. 18 170–171 (John Wiley & Sons, Ltd, 2012).
%As a person with hemophilia (PWH), my passion led me to conduct personal research to uncover the main cause of my drawbacks in my education, my career, and my romantic life. I have experienced unjustified conflicts in my social relations, feeling stale in mind and body
%Findings: Through my research, I uncovered that I used to suffer from what I call 'mind inhibitors' these were the hidden cause of my life disorders and spontaneous bleeds. These mind inhibitors are responsible for locking the body factor receptors, blocking body energy centres (like the solar plexus), discouraging the super-intelligent body cells from running their auto-healing system, and paralyzing the instinctive high-speed cellular response to external molecular treatment. 
%Mind inhibitors originate from different sources like thinking of oneself in a victim role, anxiety about medical treatments, lack of financial stability, negative attitudes, self-rejection, and contradictory thoughts and feelings. 
%Conclusion: Mind inhibitors should be handled as seriously as biological inhibitors. As Dr. Bruce Lipton explains in his book, 'The Biology of Belief'\cite{Lipton2015}: DNA does not control our biology; instead DNA is controlled by signals from outside the cell. Our bodies can be changed as we retrain our thinking, since thoughts are made of energy that affects the cellular energy level, and thus everything is created twice: once in our minds and then the physical creation follows. % 萬法唯心造
Holistic healthcare should be considered for treating patients as a complete synchronized system of soul, mind, and body; treatment should include more than medication or surgery, but a holistic approach would also address the patient's need for a subconscious paradigm shift in the person's thought and belief system.\cite{Kobisi2012}\cite{Lipton2015}

@@

In 1772, Willian Cullen, a British physician, wrote that  "I own that I did not trust much to it, but I gave it because it is necessary to give a medicine, and as what I call a placebo. If I had thought of any internal medicine it would have been a dose of the Dover's powders (made up of Ipecac and opium)."\cite{Kerr2008}\cite{Finniss2018}.
Cullen studied the objective science of analytical chemistry. He also sense that the patient's subjective, psychosomatic or "sympathetic constitution" determined his reaction to a prescribed therapeutic substance.
***Cullen developed a theory of "sympathy" (or empathy) which informed his ideas about clinical medicine dealing with psychosomatic theory of illness and mind-body therapeutics. % he do 炮製
Cullen's theory of sympathy is a mind-body function, a kind of "vital force" that animated the human body, coordinated function, and transmitted sensation to target organs\cite{Forget2003}\cite{Kerr2008}.
This finely calibrated, rational use of active placebo treatment, in which the physician dispensed a weak, physiologically active substance in order to please and calm the patient rather than to cure the patient's underlying disorder, was a product of the rational scientific culture of the 18th century Scottish Enlightenment and its embrace of a grounded, empirical approach to medicine. %啟蒙運動

@@

How does placebo effect work in patient's internal environment?  %改造患者的心，就能改造他的身體環境，有利消除癌症

@@

The anterior cingulate cortex and the dorsolateral prefrontal cortex of brain have been found to be activated by placebo administration\cite{Benedetti2005}\cite{Benedetti2011}\cite{Carlino2011}\cite{Bennett2018}. 

@@

The role of the physician was to be a gentle, sympathetic listener, who could interpret the patient's sympathetic disorder and select the proper remedy to treat it, either by prescribing placebos to please (influence the emotional states of patients), or medicine to cure the patient's disorder.

@@

The genetics of the cell give all kinds of potentials. % 自性空
Environmental signals from the cell membrane can go into the nucleus via signal transduction. The signal selectively change the reading of our gene, e.g. epigenetics regulation, controlling cell behaviors.% including genetics.
The new understanding is: environmental signals to regulatory protein to DNA to RNA and then to protein.

@@

There are studies that showed the genetic readout of some inflammatory genes in a group of people who then went through a meditation process. After 8 hours of meditation, the activity of the genes changed. 

@@

Becoming aware of the subconscious source of our behavior gives us an opportunity to change our lives by rewriting the programs (in subconscious mind) of limitation or the things that interfere with us.

@@

Of the downloaded behaviors acquired before age 7, the vast majority—70\% or more—are programs of limitation, disempowerment, and self-sabotage. These programs were acquired from other people, not from ourselves, with survival advantage.

@@

It effects on epigenetic regulation.

@@

Over 90\% of disease is a total reflection of environment and especially our programming.

@@

The mind-brain-body axis shows that subconscious fear causes releasing of inflammatory and stress hormones from brain, in terms of cell alteration in DNA methylation, mutation, mRNA expression. Carcinogenesis will occurs if the reprogramming is persistent in a longer period of time.

@@

Adverse psychosocial exposures in early life, namely experiences such as child maltreatment, caregiver stress, and community violence, have been associated in epidemiological studies with increased lifetime risk of adverse outcomes, including diabetes, heart disease, cancers, and psychiatric illnesses. Additional work has shed light on the potential molecular mechanisms by which early adversity becomes “biologically embedded” in altered physiology across body systems.\cite{Berens2017}

@@

%% TCGA new holistic features %%%%%
In summary of our current study, those 10 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in our \acrshort{hnscc} study.
Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort. The important input $X_1...X_n$ should be patients' features: age, specific 10 gene expressions, clinical T stage, and surgical margin so far.
When we consider the survival prediction model again,
ground truth Y (e.x. patient's survival):\\[0.5cm]
%Y$:\\[0.3cm]
$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$\\
gene expression is not an independent $X_{mrna}$, which could be correlated with other $X_{body}, X_{stress}, X_{fear}, X_{meaningOfLife}, X_{inflammation}, X_{ros}$ factors.
There is much work to be done in investigating the functional network more fully\cite{Rogers1959}.
%We wish the TCGA does collect more holistic features from their participants in the future.
%依舊是以管窺天
% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
%癌症與身心靈的重要關係：中醫、citation? emotional centered approach
We suggest TCGA should cover more holistic features:
cortisol is one of the most common objective outcome studied in psychoneuroimmunological (PNI) factors. Other factors usually are interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV.
The standardized, psychosocial (subjective) measures includes depression, stress, quality of life, anxiety, fatigue, mindfulness, mood and specific spiritual growth (ie, meaning of life)\cite{Hsiao2012}.
%冤親債主的意念 unknown X factors 回到我們的文章
Since psychological benefit (reduction of stress, fatigue, sleep disturbance, and depressive symptoms) also optimizes immune function (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) in terms of better survival of cancer patients.

% holistic EHR
Moreover, we encourage that physician might write their electric healthcare record (EHR) in a "holistic way".
% Deep Patient:  
Deep learning applied to EHR can derive patient representations that offer improved clinical predictions\cite{Miotto2016}
Deep learning also might convert EHR to the Fast Healthcare Interoperability Resources (FHIR) format\cite{Rajkomar2018}\cite{HealthLevelSeven2019} for handling free-text notes.
%=> Level 4 Record-keeping and Data Exchange for the healthcare process (clinical data) %Under HL7, RESTful
%Allergy, Problem,
%Procedure,
%CarePlan/Goal,
%ServiceRequest,
%Family History,
%Risk Assessment (APGAR, Glasgow coma scale)
%condition: physical, mental
%{observations: 
%vital signs, 
%body temperature, body weight and body height, 
%x-ray, 
%laboratory data, 
%pulse oximetry, 
%ECG, EEG, EMG, 
%clinical findings (symptom and sign), 
%tobacco exposure, family support, cognitive status and pregnancy status.
%death assertion
%HIV, HBV, HCV status
%}

>>>>

%=================================================================
% Journal of Personalized Medicine, JPM
\documentclass[jpm,article,submit,moreauthors,pdftex]{Definitions/mdpi}
\maxdeadcycles=1000 % Output loop---200 consecutive dead cycles.

@@

%****************%
\subsubsection{Holistic cancer care} 
% carcinogenesis by epigenetic control (placebo/nocebo), Bruce Lipton introduced mind-brain-body system. (gene expression is not an independent $X_mrna$, which is correlated with other $X_body, X_stress, X_inflammation, X_ros$)
% cancer care with person-central approach, PCA; Cullen, Carl Rogers

@@

%discussion: the third limitation
There are eighty-one ($X_1 ... X_81$) physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, 
% since it has comprehensive clinical features, 
such as age, gender, residual tumor, vital status, days\_to\_last\_followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
However, the TCGA did not collect other features from holistic cancer care.
% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equally essential comparing with physical and social status.
%
World Health Organisation has called worldwide for delivering people-centred (or person-centred) care from the physical, emotional, socioeconomic, and spiritual perspectives\cite{WHO2015}\cite{Ling-ChengMong2021}.
Core principles can be taken to achieve people-centred and integrated health service delivery. 
The first principle is holistic – focusing on physical, socioeconomic, mental, and emotional well-being. 
Holistic care has been defined that care and sees the person as a whole with psychological, social, and environmental levels of needs and goals.
%that considers  factors rather than just the symptoms of disease or ill-health.
The second principle is empowering – supporting people to manage and take responsibility for their health,
%Empowerment: the process of supporting people and communities to take control of their own health needs resulting, 
for example, in the uptake of healthier behaviors or the ability to self-manage illnesses.
People-centred care requires that people have the education and support they need to make decisions and participate in their care.
%Glossary:
%People-centred care: an approach to care that consciously adopts individuals’, carers’, families’ and communities’ perspectives as participants in, and beneficiaries of, trusted health systems that respond to their needs and preferences in humane and holistic ways. People-centred care also requires that people have the education and support they need to make decisions and participate in their own care. It is organized around the health needs and expectations of people rather than diseases (7,8) 
%Person-centred care: care approaches and practices that see the person as a whole with many levels of needs and goals, with these needs coming from their own personal social determinants of health.
%(1. World Health Organization. WHO global strategy on people-centred and integrated health services: interim report. https://apps.who.int/iris/handle/10665/155002 (2015).)

@@

Spiritual care is the key to holistic healthcare in dental practice\cite{Ling-ChengMong2021} and cancer patient care\cite{Hulett2016}. 
It is mindful of patient's mental health, emotional changes, socioeconomic during healthcare.  %Taking patient’s socioeconomic statement and supporting system thoroughly for building a holistic consideration. 
We are learning to listen proactively.
It is aware of the patient's spiritual needs.

@@

Jon Kabat-Zinn has introduced the mindfulness-Based Stress Reduction (MBSR) program in 1979\cite{Niazi2011}. MBSR composes the contemplative, spiritually based Buddhist philosophy, which promotes a nonjudgmental, accepting, and patient worldview and teaches relaxation through focused awareness on breathing during meditation. It employs (static) mindfulness meditation to alleviate suffering associated with physical (pain), psychosomatic and psychiatric disorders.

@@

These impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
Thus, cortisol is one of the most common (objective) outcomes studied in psychoneuroimmunological (PNI) factors. % others: interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV
The standardized, psychosocial (subjective) measures include depression, stress, quality of life, anxiety, fatigue, mindfulness, mood, and specific spiritual growth (i.e., the meaning of life)\cite{Hsiao2012}. %  body-mind-spirit (BMS) group therapy in the Meaning in Life questionnaire (MLQ) including two sub-scales: MLQ-Presence and MLQ-Search.

@@

This review revealed a positive pattern between spiritually-based interventions and several PNI biomarker outcomes, suggesting that spiritually-based interventions offer positive mental and physiological health benefits. For breast cancer survivors, these studies suggested that engaging in spiritually-based practices may improve or stabilize the immune profile dysregulation that occurs with breast cancer.\cite{Hulett2016}.

@@

A randomized clinical trial with active control proved that early provision of MBSR for women newly diagnosed with breast cancer provides psychological benefits (reduction of stress, fatigue, sleep disturbance, and depressive symptoms), and also optimizes immune functions (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) supportive of cancer survival\cite{WitekJanusek2019}.

%%%% PCA and ECA: the way to delivery of MBSR
The therapeutic relationship is essential towards spiritual care.
According to clinical experience in healthcare, sometimes patients could tell the physicians: "How amazing it is. I want to talk about myself more when I visit this doctor whom I trust."
In 1979, Rogers wrote: "I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing. Then simply my presence is releasing and helpful."\cite{Rogers1979}
Carl Rogers developed person-centered theory that the therapist is providing the appropriate social-environmental conditions for their patients\cite{Rogers1957}\cite{Joseph2004}\cite{Griffiths2013}.
Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers in 1957\cite{Rogers1957}:\\
%For constructive personality change to occur, it is necessary that these conditions exist and continue over a period of time: 
1. Two persons are in psychological contact. \\
2. The first, whom we shall term the client, is in a state of incongruence (or not harmony), being vulnerable or anxious. \\
3. The second person, whom we shall term the therapist, is congruent
or integrated with the relationship. \\
4. The therapist experiences "unconditional positive regard" for the client. \\
5. The therapist experiences an empathic understanding of the client's
internal frame of reference and endeavors to communicate this experience to the client. \\
6. The communication to the client of the therapist's empathic understanding and unconditional positive regard is to a minimal degree achieved.\\
%empowering
%(一)雙方有心理的接觸。
%(二)當事人正感到焦慮或不一致(incongruence)。 
%(三)治療者在治療關係中是一致的 (congruence, agreement or harmony; compatibility)、真實的或真誠的。
%(四)治療者能夠對當事人表現出無條件的關懷。無條件關懷(不批判/頓悟)
%(五)治療者能夠同理的瞭解當事人的內在，並努力傳達「我懂你的」。
%(六) 第五點只要有個適當的開始，療癒就會開始
%Dealing with negative emotions. 情緒影響，造成焦慮、發炎、免疫 Cancer
As the cancer patient feels intense negative emotions of extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, 
%七情: 喜、怒、思、悲、恐、驚、憂
depression, fatigue, stress, it is not the patient-centred therapist’s task to remove these feelings: the task is to stay with the patient’s experiences. 
% 只是陪伴
%The research implication is to investigate the necessity and sufficiency of the six conditions.
%Rogers, C. R. A Theory of Therapy, Personality, and Interpersonal Relationships: As Developed in the Client-centered Framework. in Psychology: A Study of a Science. Study 1, Volume 3: Formulations of the Person and the Social Context (ed. Koch, S.) 184–256 (McGraw Hill, 1959).\cite{Rogers1959}
%PCA理論 by *** Tex Chi
%治療關係的六核心條件: 說好話 眼對眼 engaging 用真心
%以心印心 engaging
%身心相連 body-mind connection
%捨末求本 find the source: emotion
Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection. Their empathy, sympathy, and compassion are induced by the suffering of patients from those diseases. They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner.
%身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
%「把自己當藥方開出去」
%Spirituality
%慈悲心 compassion 
%同情心 sympathy
%同理心 empathy
%non-verbal contact

@@

%% why holistic? % Environment 環境 => 分享權力、 自決 empowering
The WHO's second principle is empowering – supporting people to manage and take responsibility for their health.
Bruce Lipton introduced mind-brain-body system in 1992\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}.
%Lipton 1992, epinephrine and histamine signals in endothelium, %心智作用
In a state of fear, the brain releases chemicals of stress hormones and inflammatory cytokines.
Conversely, dopamine, oxytocin, vasopressin, and growth hormone will be released by the central nervous system in response to the perception of love.
%Bruce Lipton: the biology of belief %信念的力量 \cite{Lipton2015}
%placebo effect and the old belief of genetic determinism\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}
%biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
%那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。
%% 1. Kobisi, W. Mind inhibitors. in The 30th International Congress Of The World Federation Of Hemophilia, July 8‐12 vol. 18 170–171 (John Wiley & Sons, Ltd, 2012).
%As a person with hemophilia (PWH), my passion led me to conduct personal research to uncover the main cause of my drawbacks in my education, my career, and my romantic life. I have experienced unjustified conflicts in my social relations, feeling stale in mind and body
%Findings: Through my research, I uncovered that I used to suffer from what I call 'mind inhibitors' these were the hidden cause of my life disorders and spontaneous bleeds. These mind inhibitors are responsible for locking the body factor receptors, blocking body energy centres (like the solar plexus), discouraging the super-intelligent body cells from running their auto-healing system, and paralyzing the instinctive high-speed cellular response to external molecular treatment. 
%Mind inhibitors originate from different sources like thinking of oneself in a victim role, anxiety about medical treatments, lack of financial stability, negative attitudes, self-rejection, and contradictory thoughts and feelings. 
%Conclusion: Mind inhibitors should be handled as seriously as biological inhibitors. As Dr. Bruce Lipton explains in his book, 'The Biology of Belief'\cite{Lipton2015}: DNA does not control our biology; instead DNA is controlled by signals from outside the cell. Our bodies can be changed as we retrain our thinking, since thoughts are made of energy that affects the cellular energy level, and thus everything is created twice: once in our minds and then the physical creation follows. % 萬法唯心造
Holistic healthcare should be considered for treating patients as a complete synchronized system of soul, mind, and body; treatment should include more than medication or surgery, but a holistic approach would also address the patient's need for a subconscious paradigm shift in the person's thought and belief system.\cite{Kobisi2012}\cite{Lipton2015}

@@

In 1772, Willian Cullen, a British physician, wrote that  "I own that I did not trust much to it, but I gave it because it is necessary to give a medicine, and as what I call a placebo. If I had thought of any internal medicine, it would have been a dose of the Dover's powders (made up of Ipecac and opium)."\cite{Kerr2008}\cite{Finniss2018}.
Cullen studied the objective science of analytical chemistry. He also sensed that the patient's subjective, psychosomatic, or "sympathetic constitution" determined his reaction to a prescribed therapeutic substance.
Cullen developed a theory of "sympathy" (or empathy) which informed his ideas about clinical medicine dealing with the psychosomatic theory of illness and mind-body therapeutics. % he do 炮製
Cullen's theory of sympathy is a mind-body function, a kind of "vital force" that animated the human body, joint function, and transmitted sensation to target organs\cite{Forget2003}\cite{Kerr2008}.
This finely calibrated, rational use of active placebo treatment, in which the physician-dispensed weak, physiologically active substance in order to please and calm the patient rather than to cure the patient's underlying disorder, was a product of the rational scientific culture of the 18th century Scottish Enlightenment and its embrace of a grounded, empirical approach to medicine. %啟蒙運動

@@

%How does placebo effect work in patient's internal environment?  %改造患者的心，就能改造他的身體環境，有利消除癌症

@@

The anterior cingulate cortex and the dorsolateral prefrontal cortex of the brain have been found to be activated by placebo administration\cite{Benedetti2005}\cite{Benedetti2011}\cite{Carlino2011}\cite{Bennett2018}. 

@@

The physician's role was to be a gentle, sympathetic listener who could interpret the patient's sympathetic disorder and select the proper remedy to treat it, either by prescribing placebos to please (influence the patients' emotional states) medicine to cure the patient's disorder.

@@

The genetics of the cell gives all kinds of potentials. % 自性空
Environmental signals from the cell membrane can go into the nucleus via signal transduction. The signal selectively changes the reading of our gene, e.g., epigenetics regulation, controlling cell behaviors.% including genetics.
The new understanding is environmental signals to regulatory protein to DNA to RNA and then to protein.

@@

Some studies showed the genetic readout of some inflammatory genes in a group of people who went through a meditation process. After 8 hours of meditation, the activity of the genes changed. 

@@

Becoming aware of our behavior's subconscious source allows us to change our lives by rewriting the programs (in the subconscious mind) of limitation or the things that interfere with us.

@@

Of the downloaded behaviors acquired before age 7, the vast majority—70\% or more—are programs of limitation, disempowerment, and self-sabotage. These programs were acquired from other people, not from ourselves, with a survival advantage.

@@

It affects epigenetic regulation.

@@

Over 90\% of disease is a total reflection of the environment and especially our programming.

@@

The mind-brain-body axis shows that subconscious fear causes releasing of inflammatory and stress hormones from the brain in terms of cell alteration in DNA methylation, mutation, mRNA expression. Carcinogenesis will occur if the reprogramming is persistent for a longer time.

@@

Adverse psychosocial exposures in early life, namely experiences such as child maltreatment, caregiver stress, and community violence, have been associated in epidemiological studies with an increased lifetime risk of adverse outcomes, including diabetes, heart disease, cancers, and psychiatric illnesses. Additional work has shed light on the potential molecular mechanisms by which early adversity becomes "biologically embedded" in altered physiology across body systems.\cite{Berens2017}

@@

%% TCGA new holistic features %%%%%
Our current study summarizes those six candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in our \acrshort{hnscc} study.
Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort. The important input $X_1...X_n$ should be patients' features: age, specific six gene expressions, clinical T stage, and surgical margin so far.
When we consider the survival prediction model again,
ground truth Y (e.x. patient's survival):\\[0.5cm]
%Y$:\\[0.3cm]
$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$\\
gene expression is not an independent $X_{mrna}$, which could be correlated with other $X_{body}, X_{stress}, X_{fear}, X_{meaningOfLife}, X_{inflammation}, X_{ros}$ factors.
There is much work to be done in investigating the functional network more fully\cite{Rogers1959}.
%We wish the TCGA does collect more holistic features from their participants in the future.
%依舊是以管窺天
% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
%癌症與身心靈的重要關係：中醫、citation? emotional centered approach
We suggest TCGA should cover more holistic features:
cortisol is one of the most common objective outcomes studied in psychoneuroimmunological (PNI) factors. Other factors are interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV.
The standardized, psychosocial (subjective) measures include depression, stress, quality of life, anxiety, fatigue, mindfulness, mood, and specific spiritual growth (i.e., the meaning of life)\cite{Hsiao2012}.
%冤親債主的意念 unknown X factors 回到我們的文章
Since psychological benefit (reduction of stress, fatigue, sleep disturbance, and depressive symptoms) also optimizes immune function (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) in terms of better survival of cancer patients.

% holistic EHR
Moreover, we encourage physicians to write their electric healthcare record (EHR) in a "holistic way".
% Deep Patient:  
Deep learning applied to EHR can derive patient representations that offer improved clinical predictions\cite{Miotto2016}
Deep learning also might convert EHR to the Fast Healthcare Interoperability Resources (FHIR) format\cite{Rajkomar2018}\cite{HealthLevelSeven2019} for handling free-text notes.
%=> Level 4 Record-keeping and Data Exchange for the healthcare process (clinical data) %Under HL7, RESTful
%Allergy, Problem,
%Procedure,
%CarePlan/Goal,
%ServiceRequest,
%Family History,
%Risk Assessment (APGAR, Glasgow coma scale)
%condition: physical, mental
%{observations: 
%vital signs, 
%body temperature, body weight and body height, 
%x-ray, 
%laboratory data, 
%pulse oximetry, 
%ECG, EEG, EMG, 
%clinical findings (symptom and sign), 
%tobacco exposure, family support, cognitive status and pregnancy status.
%death assertion
%HIV, HBV, HCV status
%}
